---
title : Shiny Project for Developing Data Product Course
subtitle: Predicting Miles Per Gallon
author: PeterH8
framework: io2012
highlighter: highlight.js
hitheme: tomorrow
widgets: [mathjax]
mode: selfcontained
---

## Problem Definition and Approach

1. Used the `mtcars` dataset in R `datasets` 
2. Trained a linear model for predicting `mpg` (Miles/(US) gallon) from other variables
3. Did model selection by applying stepAIC on initial model `mpg ~ .`
4. Selected `mpg ~ wt + qsec + am`.
5. Reporeted summary of fitted model.
6. User providing values for `wt`, `qsec`, and `am` to do prediction.

---

## Model Selection

```{r modelselection, echo=TRUE, cache=TRUE, results='hide'}
library(MASS)
step <- stepAIC(fit6, direction="backward");
```
```{r modelselectionanova, echo=TRUE, cache=TRUE}
print(step$anova)
```

---

## Retrain selected Model

```{r retrainining, echo=TRUE, cache=TRUE, messages=FALSE}
fit <- lm(mpg ~ wt + qsec + am, data=mtcars);
print(summary(fit))
```

---

## Example of Prediction and Pointers

```{r prediction, echo=TRUE, cache=TRUE}
mpgPrediction <- function(df) predict(fit, newdata=df)[[1]]
cat("Prediction of (wt=3.3, qsec=17.7, am = 'Automatic'):", 
    mpgPrediction(data.frame(wt=3.3, qsec=17.7, am=0)))
```
1. The Application can be found [here](http://peterh8.shinyapps.io/Course_Project/).
2. The R code can be found at [my github repository](https://github.com/PeterH8/DevDataProd_ShinyProject).

